Cognate beginnings to bilingual lexical acquisition

### 2023-07-26 docs/index.qmd
Update Dockerfile

```{r setup}
#| label: setup
#| message: false
#| warning: false
# load objects -----------------------------------------------------------------
targets::tar_config_set(
    store = here::here("_targets"),
    script = here::here("_targets.R")
)

@@

@@

@@

# Links

![arXiv](https://info.arxiv.org/brand/images/brand-logo-primary.jpg){height="100px"}

![OSF](https://www.datacc.org/wp-content/uploads/2020/03/osf.png){height="100px"}

![GitHub](https://upload.wikimedia.org/wikipedia/commons/thumb/9/91/Octicons-mark-github.svg/2048px-Octicons-mark-github.svg.png){height="100px"}

>>>>

# Cognate beginnings to bilingual lexical acquisition

```{r setup}
#| label: setup
#| message: false
#| warning: false
#| echo: false
# load objects -----------------------------------------------------------------
targets::tar_config_set(
    store = here::here("_targets"),
    script = here::here("_targets.R")
)

@@

## Abstract

@@

## Acknowledgements

@@
